Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-19 cordillera-cycle.tex
Rename figure lr_ts_deglac to hr_ts_deglac.

      In our simulations, the timing of peak ice volume during the LGM and
      the pacing of deglaciation depend critically on the choice of climate
      forcing (Table~\ref{tab:extrema}; Figs.~\ref{fig:lr_ts}
      and~\ref{fig:lr_ts_deglac}). Adopting the EPICA climate forcing yields
      peak ice volume at 17.2\,\unit{ka} and an uninterrupted deglaciation
      until about 9\,\unit{ka} (Fig.~\ref{fig:lr_ts_deglac}, lower panel,
      red curves). On the contrary, the simulation driven by the GRIP
      palaeo-temperature record yields peak ice volume at 19.3\,\unit{ka}
      and a~deglaciation interrupted by two phases of regrowth until about
      8\,\unit{ka}. The first interruption occurs between 16.6 and
      14.5\,\unit{ka}, and the second between 13.1 and 11.6\,\unit{ka}
      (Fig.~\ref{fig:lr_ts_deglac}, lower panel, blue curve).

@@

\begin{figure}%
\includegraphics{lr_ts_deglac}
\caption{%
      Temperature offset time-series from the GRIP and EPICA ice core
      records (Table~\ref{tab:records}) (top panel), and modelled ice volume
      during the deglaciation, expressed in meters of sea-level equivalent
      (bottom panel).}
\label{fig:lr_ts_deglac}%
\end{figure}%

>>>>

      In our simulations, the timing of peak ice volume during the LGM and
      the pacing of deglaciation depend critically on the choice of climate
      forcing (Table~\ref{tab:extrema}; Figs.~\ref{fig:lr_ts}
      and~\ref{fig:hr_ts_deglac}). Adopting the EPICA climate forcing yields
      peak ice volume at 17.2\,\unit{ka} and an uninterrupted deglaciation
      until about 9\,\unit{ka} (Fig.~\ref{fig:hr_ts_deglac}, lower panel,
      red curves). On the contrary, the simulation driven by the GRIP
      palaeo-temperature record yields peak ice volume at 19.3\,\unit{ka}
      and a~deglaciation interrupted by two phases of regrowth until about
      8\,\unit{ka}. The first interruption occurs between 16.6 and
      14.5\,\unit{ka}, and the second between 13.1 and 11.6\,\unit{ka}
      (Fig.~\ref{fig:hr_ts_deglac}, lower panel, blue curve).

@@

\begin{figure}%
\includegraphics{hr_ts_deglac}
\caption{%
      Temperature offset time-series from the GRIP and EPICA ice core
      records (Table~\ref{tab:records}) (top panel), and modelled ice volume
      during the deglaciation, expressed in meters of sea-level equivalent
      (bottom panel).}
\label{fig:hr_ts_deglac}%
\end{figure}%
